---
title: "R Markdown Template"
author: "Your Name"
date: "2024-12-05"
output:
  pdf_document: default
---

This is an R Markdown template that outlines minimal reproducibility suggestions for the GWD thesis writers.

# Dependencies

Describe any dependencies needed to execute your code. 

### Data and Folders

Example: The data is stored in the "data.txt" file in the "data" folder.

```{r folders, include=FALSE}
# Folders
dir.create("data", showWarnings = FALSE)
dir.create("figures", showWarnings = FALSE)
dir.create("output", showWarnings = FALSE)
```

Any files in the "output" folder that are read in using readRDS() should be mentioned here.

### System

List any system dependencies needed to execute your code. 

```yaml
dependencies:
  - R>=4.1  # https://www.r-project.org/
```

```{r version, include=FALSE}
# Check the version
R.Version()$version.string
```


### R Packages

Install and load packages simultaneously with the **pacman** package.

```{r packages, echo=TRUE}
# Packages
if (!require(pacman)) install.packages("pacman")
pacman::p_load(tidyverse, brms, latex2exp)

# If you get the error "! LaTeX Error: File `framed.sty' not found." when rendering,
# uncomment and run the following 2 lines.
#install.packages(c('tinytex', 'rmarkdown'))
#tinytex::install_tinytex()
```

# Code

The code to produce all tables, figures, etc. in your thesis goes here.

### Modeling

If you run computationally intensive procedures (e.g., Bayesian hierarchical models, spatial data, etc.), you can use saveRDS() and readRDS() to save and read back in output.

```{r brmssave, eval=FALSE}
# Example adapted from http://paulbuerkner.com/brms/

fit1 <- brm(count ~ zAge + zBase * Trt + (1 | patient),
            data = epilepsy, family = poisson(), chains = 2, 
            iter = 550, cores = 2, warmup = 50)

saveRDS(fit1, "output/fit1.RDS")
```

```{r brmsread, eval = TRUE, echo=TRUE}
# Extract model output without rerunning each time

fit1 <- readRDS("output/fit1.RDS")
post_sum <- posterior_summary(fit1)
```

### Figures

Display your figures in the generated pdf and save them in the "figures" folder for use in your thesis. The **latex2exp** package is useful for figure labels because it allows you type in the LaTex syntax.

```{r figure, fig.width=6, fig.height=4, echo=FALSE}
post.samples <- as_draws_matrix(fit1)
figure1 <- ggplot(post.samples) + 
  geom_line(aes(x = c(1:nrow(post.samples)), y = Intercept)) +
  labs(x = "Iteration", y = "Posterior Draw", 
       title = latex2exp::TeX(r"( Traceplot for the intercept ($\beta_0$) )")) + 
  theme_bw()

# Save the figure as a pdf, png, jpg, etc.
ggsave("figures/traceplot.pdf", figure1, width = 8, height = 6) 

# Display the graphic when rendering
show(figure1)
```






